\title{A Very Simple \LaTeXe{} Template}
\author{
        John E. Palenchar \\
                Department of Mathamatics\\
        Student---University of Florida\\
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}
\maketitle

This starts the second part of the course.\\
Induction \\
First group of induction arguments. \\
Second group Strong induction \\
Third group Proof by considering the least counterexample. \\
\\Simple Induction Proving statements of the form $\forall n \in \mathbb{N} P(n)$
\\basis steps: $P(0)$
\\induction step: $\forall n \in \mathbb{N} (P(n) \rightarrow P(n+1))$
\\conclude that  $ \forall n P(n)$ holds
\\Strong induction: Proving statements $\forall n \in \mathbb{N} P(n)$
\\Prove $\forall n ( \forall m < n P(m)) \rightarrow P(n)$
\\conclude $\forall n P(n) $ holds\\

Proof by least counterexample: proving $\forall n \in \mathbb{N} P(n)$\\
argue by contradiction.
Assume that $P(n)$ fails for some $n$.
Let $n$ be smallest such that $P(n)$ fails. get a contradiction.


Simple induction proof.\\
Summation Formulas:
\\ \underbar{Th.} For every Number $n \in \mathbb{N}$
\\ $0+1+2+3+\dots+n = \frac{n(n+1)}{2}$
\\please rewrite as $\sum_{k=0}^{n} k = \frac{n(n+1)}{2}$
\\ \underbar{Proof.}
\\ basis step $\sum_{k=0}^{0} k = 0 = \frac{0(0+1)}{2}$
\\ induction step. Opponent hands you $n  \in \mathbb{N}$
say $P(n)$ holds you need to conclude that $P(n+1)$ holds.

The induction hypothesi in this case that 
$\sum_{k=0}^{n} k = \frac{n(n+1)}{2}$
$\sum_{k=0}^{n+1}k = \sum_{k=0}^{n}x +n+1 = \frac{n(n+1)}{2}+n+1 = \frac{(n+1)(n+2)}{2}$\\
\begin{flushright}
        $\Box$
\end{flushright}

\underbar{Th.} For every number $n \in \mathbb{N}$
$1+3+5+\dots+(2n+1) = (n+1)^2$
\\rewrite $\sum_{k=0}^{n} (2k+1) = (n+1)^2$\\

\underbar{Proof.} This is the proof
\\basis step: $\sum_{k=0}^{0}(2k+1) = 1 = (0+1)^2$
\\ induction step: Opponent hands you $n  \in \mathbb{N}$ 
say $P(n)$ holds you need to conclude that $P(n+1)$ holds.\\

$\sum_{k=0}^{n}(2k+1) = (n+1)^2$
\\
\\
$\sum_{k=0}^{n+1}(2k+1)= \sum_{k=0}^{n}(2k+1)+2n+1+1 = (n+1)^2 +2n+1=(n+2)^2$
\begin{flushright}
        $\Box$
\end{flushright}


\underbar{Strong Induction:}
Fibonacci Numbers.\\
Defined by recursion:\\
$F_0 = 0 ,F_1 = 1,F_{n+2} = F_n +F_{n+1}$\\
Example $0,1,1,2,3,5,8$

\underbar{Th.} for every $n\in \mathbb{N} F_n < 2^n$
\\ Proof: assume that this has been checked for all values up to $n >= 2$
\\We need to conclude that it is true at $n$ as well\\
$F_n = F_{n-1} +F_{n-2} <2^{n-1}+2^{n-2} <2(2^{n-1}) = 2^n$\\
$F_{n-1} <2^{n-1} $ $f_{n-2} < 2^{n-2} $
\begin{flushright}
        $\Box$
\end{flushright}

other proof for same problem 

\underbar{Proof.}\\
BWOC lest n be smallest n such that $F_n >= 2^n$
check that $n != 0$ and $n!= 1$
It has to be that $F_n = F_{n-1}+F_{n-2}<n^{n-1}+2^{n-2}\dots < 2^n$
This is a contradiction with the initial assumption on $n$.
\begin{flushright}
        $\Box$
\end{flushright}
\end{document}
